
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand\mybar{\kern1pt\rule[-\dp\strutbox]{.8pt}{\baselineskip}\kern1pt}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{milesbarrios.dev}{\Large Miles Barrios}} \\ 
  602-828-9896 \mid \href{mailto:contact@milesbarrios.dev}{contact@milesbarrios.dev} \mid 
  \href{https://github.com/milesbarrios}{GitHub} \mid \href{https://www.linkedin.com/in/miles-barrios/}{LinkedIn} \mid \href{https://milesbarrios.dev}{milesbarrios.dev}  \\
\end{tabular*}

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Java, Javascript, HTML, CSS, C, Python}
     \hfill
   }
   \item{
   \textbf{Technologies}{: NodeJS, React, VSCode Ext, REST APIs,}
   }
 \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Northern Arizona University}{Flagstaff, AZ}
      {Bachelor of Science in Computer Science;  GPA: 3.64}{Aug. 2017 -- May. 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {State Farm}{Tempe, AZ}
      {Enterprise Technology Intern}{August 2020 - Present}
      \resumeItemListStart
        \item
            \textbf{}{Interned on the Availability Management Tooling team in infrastructure}
        \item
            \textbf{}{Worked with multiple open source technologies including the Elastic Stack, Docker, Kibana, Selenium, and Jenkins}
       \resumeItemListEnd
       
       \resumeSubheading
      {Northern Arizona University}{Flagstaff, AZ}
      {Teaching Assistant}{January 2020 - Present}
      \resumeItemListStart
        \item
            \textbf{}{Performed grading for student assignments in Data Structures, Computer Science II, and Operating Systems}
        \item
            \textbf{}{Delivered in office student assistance for project related Data Structures course work at NAU}
      \resumeItemListEnd
       
       
    \resumeSubheading
      {State Farm}{Tempe, AZ}
      {Enterprise Technology Intern}{May 2020 - July 2020}
      \resumeItemListStart
        \item
            \textbf{}{Contributor on customer facing software development team with focus on development of a VSCode extension pack for developers}
        \item
            \textbf{}{Extension project completed using Javascript, HTML, and CSS}
        \item
            \textbf{}{Utilized scrum methodology in an agile environment}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{StateFarm Hackday Project}
      {React application that tracks code reviews for gitlab users in all groups and all projects within those groups. Utilized React and Axios to grab the merge requests and display on a single-page application.}
    \resumeSubItem{Software Engineering Semester Project}
      {Developed a campus social media mobile application aimed towards helping freshman and international students meet others on campus. Developed in Flutter using the Dart programming language.}
     \resumeSubItem{Operating System Simulator}
        {Over the course of the semester, developed a non-trivial project that simulated an operating system. Developed using C and practiced the use of PCBs, memory management, and concurrency.}

  \resumeSubHeadingListEnd
  
  %-----------Hobbies----------------
  \section{Hobbies}
    \resumeSubHeadingListStart
       \begin{itemize}
           \item \textbf{}{Mountain Biking}
           \item \textbf{}{Disc Golf}
           \item \textbf{}{Hiking}
           \item \textbf{}{Video Games}
       \end{itemize}
    \resumeSubHeadingListEnd

%------------------------------------------
%
\end{document}
